NFL Draft Analysis

### 2020-05-12 draft_analysis.Rmd
Reformatted titles for some graphs

grid.arrange(qb_bar, rb_bar, wr_bar, ncol=3, top = "Average Value in Different Rounds over the 2000s")
```

@@

rb_violin <- master_df %>%
  filter(year >= 2000) %>%
  filter(Pos == "RB") %>%
  ggplot(mapping=aes(x=factor(Rnd), y=CarAV)) +
    geom_violin()  +
    labs(x = "Rnd", y = "Career Value", title = "Average Value over Round for RBs") + 
    geom_smooth(method=lm)

wr_violin <- master_df %>%
  filter(year >= 2000) %>%
  filter(Pos == "WR") %>%
  ggplot(mapping=aes(x=factor(Rnd), y=CarAV)) +
    geom_violin()  +
    labs(x = "Rnd", y = "Career Value", title = "Average Value over Round for WRs") + 
    geom_smooth(method=lm)

grid.arrange(qb_violin, rb_violin, wr_violin, ncol=3, top = "Average Value over Round")
```

>>>>

grid.arrange(qb_bar, rb_bar, wr_bar, ncol=3, top = "Average Value in Different Rounds in the 2000s")
```

@@

qb_violin <- master_df %>%
  filter(year >= 2000) %>%
  filter(Pos == "QB") %>%
  ggplot(mapping=aes(x=factor(Rnd), y=CarAV)) +
    geom_violin()  +
    labs(x = "Rnd", y = "Career Value", title = "QB Average Value") + 
    geom_smooth(method=lm)

rb_violin <- master_df %>%
  filter(year >= 2000) %>%
  filter(Pos == "RB") %>%
  ggplot(mapping=aes(x=factor(Rnd), y=CarAV)) +
    geom_violin()  +
    labs(x = "Rnd", y = "Career Value", title = "RB Average Value") + 
    geom_smooth(method=lm)

wr_violin <- master_df %>%
  filter(year >= 2000) %>%
  filter(Pos == "WR") %>%
  ggplot(mapping=aes(x=factor(Rnd), y=CarAV)) +
    geom_violin()  +
    labs(x = "Rnd", y = "Career Value", title = "WR Average Value") + 
    geom_smooth(method=lm)

grid.arrange(qb_violin, rb_violin, wr_violin, ncol=3, top = "Average Value over Round in the 2000s")
```
